---
title: ""
output: 
  html_document:
    df_print: paged
params: 
  User.email: ""
  User.name: ""
date: "`r Sys.Date()`"
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```
<!-- TODO: upload logo file -->
<div style="text-align: center;">
<img src=/Users/HGL_logo.png alt="HGL." width="400" height="400">
</div>
# SAT Initial Diagnostic Score Report
## `r params$User.name`

Your SAT score is calculated from the four test modules across two sections: Reading and Writing and Math. The raw points (total number of correct answers) from each module are converted into a scaled score, which adds to a maximum of 1600 points. There are 800 points available in Reading and Writing and 800 in Math. Your composite and section scores on this diagnostic are reported as a range due to the adaptive nature of the digital SAT and the unknowns inherent to the SAT's proprietary algorithms. 													

```{r libraries}

library(DT)
library(knitr)
library(tidyverse)
library(kableExtra)
library(ggstance)
library(broom)
library(lme4)
library(dplyr)
library(plotly)
library(ggplot2)
library(ggalt)
library(ggdist)

setwd("Users/Downloads/rfiles/")

full_comb <- read.csv("./Ouptput_Files/full_comb.csv")

full_comb <- full_comb %>% 
  select(-X)

raw_scaled <- read.csv("./Input_Files/Raw and Scaled Scores SAT Pretest.csv")
```


```{r Composite Score Table - student specific}

#raw points table for RWM1 and RWM2
RWM1_data <- full_comb %>%
  filter(Source == "RWM1", User.email == params$User.email)

RWM1_rawscore <- data.frame(
  Attribute = c("Raw Points"), 
  Points = sum(RWM1_data$Point)
  )

RWM2_data <- full_comb %>%
  filter(Source == "RWM2", User.email == params$User.email)

RWM2_rawscore <- data.frame(
  Attribute = c("Raw Points"), 
  Points = sum(RWM2_data$Point)
  )

##combined RWM Score Range

RWM_sum <- sum(RWM1_rawscore$Points, RWM2_rawscore$Points) ##use when running normal per student

# RWM_sum <- (sum(RWM1_rawscore$Points, RWM2_rawscore$Points))/10 ##Use for class-level.  Delete divisor

# Convert R.W.Raw and R.W.Scale.Low to numeric
raw_scaled$R.W.Raw <- as.numeric(raw_scaled$R.W.Raw)
raw_scaled$R.W.Raw <- as.numeric(raw_scaled$R.W.Raw.1)
raw_scaled$R.W.Scale.Low <- as.numeric(raw_scaled$R.W.Scale.Low)
raw_scaled$R.W.Scale.High <- as.numeric(raw_scaled$R.W.Scale.High)

###low range
# Find the index of the closest value in R.W.Raw to RWM_sum
index_RWM1 <- which.min(abs(raw_scaled$R.W.Raw - RWM_sum))
# Retrieve the corresponding R.W.Scale.Low value
RWM_low <- raw_scaled$R.W.Scale.Low[index_RWM1]

### high range
index_RWM2 <- which.min(abs(raw_scaled$R.W.Raw.1 - RWM_sum))

RWM_high <- raw_scaled$R.W.Scale.High[index_RWM2]

#making Reading and writing Score Range Table
RWM_score_range <- data.frame(
  Low = (RWM_low),
  High = (RWM_high)
)

RWM_score_range_table <- RWM_score_range %>%
  kbl(format = "html", escape = FALSE) %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c("Reading and Writing Score Range" = 2)) %>%
  row_spec(0, background = "#00AEEE")


```

``` {r Math tables}
#Math raw and scaled scores tables
#raw points table for MM1
MM1_data <- full_comb %>%
  filter(Source == "MM1", User.email == params$User.email)

total_math_points1 <- sum(MM1_data$Point)

Mult_choice_math <- sum(MM1_data$Point[!grepl("SPR", MM1_data$Question.Domain)])

SPR <- sum(MM1_data$Point[grepl("SPR", MM1_data$Question.Domain)])

MM1_rawscore <- data.frame(
  Attribute = c("Raw Score", "Multiple Choice Raw", "Student-Produced Response Raw"),
  Points = c(total_math_points1, Mult_choice_math, SPR)
)

MM1_rawscore_table <- MM1_rawscore %>% 
  kbl(format = "html", escape = FALSE) %>% 
  kable_styling(full_width = FALSE) %>% 
  add_header_above(c("Math Module 1" = 2), background = "#00AEEE")

#raw points table for MM2
MM2_data <- full_comb %>%
  filter(Source == "MM2", User.email == params$User.email)

total_math_points2 <- sum(MM2_data$Point)

Mult_choice_math2 <- sum(MM2_data$Point[!grepl("SPR,|SPR", MM2_data$Question.Domain)])

SPR2 <- sum(MM2_data$Point[grepl("SPR,|SPR", MM2_data$Question.Domain)])

MM2_rawscore <- data.frame(
  Attribute = c("Raw Score", "Multiple Choice Raw", "Student-Produced Response Raw"),
  Points = c(total_math_points2, Mult_choice_math2, SPR2)
)

MM2_rawscore_table <- MM2_rawscore %>% 
  kbl(format = "html", escape = FALSE) %>% 
  kable_styling(full_width = FALSE) %>% 
  add_header_above(c("Math Module 2" = 2), background = "#00AEEE")

##combined MM Score Range

MM1_sum <- MM1_rawscore %>% 
  filter(Attribute == "Raw Score")
               
MM2_sum <- MM2_rawscore %>% 
  filter(Attribute == "Raw Score")

MM_sum <- sum(MM1_sum$Points, MM2_sum$Points)

#Working with the scores
# Convert Math.Raw and Math.Scale.Low to numeric
raw_scaled$Math.Raw <- as.numeric(raw_scaled$Math.Raw)
raw_scaled$Math.Raw <- as.numeric(raw_scaled$Math.Raw.1)
raw_scaled$Math.Scale.Low <- as.numeric(raw_scaled$Math.Scale.Low)
raw_scaled$Math.Scale.High <- as.numeric(raw_scaled$Math.Scale.High)

###low range
# Find the index of the closest value in Math.Raw to MM_sum
index_MM1 <- which.min(abs(raw_scaled$Math.Raw - MM_sum))
# Retrieve the corresponding R.W.Scale.Low value
MM_low <- raw_scaled$Math.Scale.Low[index_MM1]

### high range
index_MM2 <- which.min(abs(raw_scaled$Math.Raw.1 - MM_sum))

MM_high <- raw_scaled$Math.Scale.High[index_MM2]

#Making math score range table
MM_score_range <- data.frame(
  Low = (MM_low),
  High = (MM_high)
)

MM_score_range_table <- MM_score_range %>% 
  kbl(format = "html", escape = FALSE) %>% 
  kable_styling(full_width = FALSE) %>% 
  add_header_above(c("Math Score Range" = 2)) %>% 
  row_spec(0, background = "#00AEEE")

```
# Score Tables

``` {r Comp tables}

Comp_score_low <- sum(RWM_score_range$Low, MM_score_range$Low)

Comp_score_high <- sum(RWM_score_range$High, MM_score_range$High)

Comp_score_range <- data.frame(
  Low = (Comp_score_low),
  High = (Comp_score_high)
)

Comp_score_range_table <- Comp_score_range %>% 
  kbl(format = "html", escape = FALSE) %>% 
  kable_styling(full_width = FALSE) %>% 
  add_header_above(c("Composite Score Range" = 2)) %>% 
  row_spec(0, background = "#00AEEE")

```

```{r comp tables}

Comp_score_range_table
RWM_score_range_table
MM_score_range_table

```


# Reading and Writing Modules {.tabset}
## Reading and Writing Question Domain Accuracy
```{r - RW Question Domain Accuracy Graph, out.width='100%'}
combined_RWM <- bind_rows(RWM1_data, RWM2_data)

accuracy_RWM <- combined_RWM %>% 
  group_by(Question.Domain) %>% 
  summarize(
    Accuracy = round(sum(Point)/n() *100, digits = 0)
  ) 

 #setting Question Domain as a factor level var
# accuracy_RWM$`Question Domain` <- factor(accuracy_RWM$`Question Domain`, levels = unique(accuracy_RWM$`Question Domain`))
# 
# #setting Accuracy as a continuous variable
# accuracy_RWM$Accuracy <- as.numeric(gsub("%", "", accuracy_RWM$Accuracy))

RWM1_horizontal_lollipop_plot <- ggplot(accuracy_RWM, aes(x = Accuracy, y = Question.Domain)) +
  geom_segment(aes(xend = 0, yend = Question.Domain), color = "#00AEEE", size = 2) +  # Create the lollipops with horizontal segments
  geom_point(aes(x = Accuracy, y = Question.Domain), color = "#506171", size = 4) +
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 25)) +  # Set x-axis limits and breaks
  labs(x = "Accuracy (%)", y = NULL, title = "Question Domain Accuracy") +  # Set axis labels and title
  theme_minimal() +  # Apply a minimal theme
     theme(
    axis.title = element_text(size = 16),  # Adjust axis label size
    axis.text = element_text(size = 14),  # Adjust axis tick label size
    plot.title = element_text(size = 20, face = "bold"),  # Adjust title size
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10)  # Adjust margin for plot spacing
    # plot.title.position = "plot"
  ) +
  geom_point(color = "#506171", size = 4)  # Add circles at the end of the horizontal segments

((ggplotly(RWM1_horizontal_lollipop_plot)))

```

**Question Domain** 
*Craft and Structure*
Students will use comprehension, vocabulary, analysis, synthesis, and reasoning skills and knowledge to use and determine the meaning of high-utility academic words and phrases in context, evaluate texts rhetorically, and make supportable connections between multiple topically related texts – in the latter students will answer a single question comparing two short texts. 

*Information and Ideas*
Students will use comprehension, analysis, and reasoning skills and knowledge as well as what is stated and implied in texts (including any informational graphics) to locate, interpret, evaluate, and integrate information and ideas.

*Standard English Conventions*
Students will use editing skills and knowledge to make a text conform to core conventions of Standard English, sentence structure, usage, and punctuation.

*Expression of Ideas*
Students will use revision skills and knowledge to improve the effectiveness of written expression in accordance with specified rhetorical goals. 
# {-}

## Reading and Writing Module 1 

```{r - RWM1 Table, echo = FALSE, results = 'asis'}
#creating dataframe for the raw score for this section
 RWM1_data <- full_comb %>%
   filter(Source == "RWM1", User.email == params$User.email)

RWM1_rawscore <- data.frame(
  Attribute = c("Raw Score"), 
  Points = sum(RWM1_data$Point)
  )

#Remove column names and convert to a matrix
table_matrix1 <- RWM1_rawscore %>% 
  column_to_rownames(var = "Attribute") %>% 
  as.matrix()

table_matrix1 %>% 
  kbl(format = "html") %>% 
  kable_styling(full_width = FALSE) %>% 
  add_header_above(c("Reading and Writing Module 1" = 2)) %>% 
  row_spec(0, background = "#00AEEE")

#Dropping User.email from table
RWM1_scores <- RWM1_data %>%
  select(-(c(User.email, User.name, Source)))

RWM1_scores %>% 
  kbl(format = "html", escape = FALSE) %>% 
  kable_styling (full_width = T, "striped")%>%
  row_spec(0, background = "#00AEEE") %>%
  row_spec(0:27, align = "c") %>% 
  column_spec(1, bold = T) %>% 
  column_spec(2, background = "#9FE2BF") %>% 
  column_spec(4, background = case_when((RWM1_scores$Point == 0) ~ "#F88379", TRUE ~ "white"))
```

## Reading and Writing Module 2
```{r - RWM2 Table}
#creating dataframe for the raw score for this section

RWM2_data <- full_comb %>%
  filter(Source == "RWM2", User.email == params$User.email)

RWM2_rawscore <- data.frame(
  Attribute = c("Raw Score"), 
  Points = sum(RWM2_data$Point)
  )

#Remove column names and convert to a matrix
table_matrix2 <- RWM2_rawscore %>% 
  column_to_rownames(var = "Attribute") %>% 
  as.matrix()

table_matrix2 %>% 
  kbl(format = "html") %>% 
  kable_styling(full_width = FALSE) %>% 
  add_header_above(c("Reading and Writing Module 2" = 2)) %>% 
  row_spec(0, background = "#00AEEE")

#Dropping User.email from table
RWM2_scores <- RWM2_data %>%
  select(-(c(User.email, User.name, Source)))

RWM2_scores %>% 
  kbl(format = "html", escape = FALSE) %>% 
  kable_styling (full_width = T, "striped")%>%
  row_spec(0, background = "#00AEEE") %>%
  row_spec(0:27, align = "c") %>% 
  column_spec(1, bold = T) %>% 
  column_spec(2, background = "#9FE2BF") %>% 
  column_spec(4, background = case_when((RWM2_scores$Point == 0) ~ "#F88379", TRUE ~ "white"))
```

# Math Modules {.tabset}
## Math Question Domain Accuracy
```{r - Math Question Domain Accuracy Graph - MC and SPR, out.width='100%'}
combined_MM <- bind_rows(MM1_data, MM2_data)

combined_MM <- combined_MM %>%
  mutate(Category = ifelse(grepl("SPR", Question.Domain), "SPR", "Multiple Choice"))

# Aggregate data for "Multiple Choice" and "SPR"
aggregate_data <- combined_MM %>%
  group_by(Category) %>%
  summarise(Accuracy = mean(Point) * 100)

# Plot lollipop chart for "Multiple Choice" and "SPR"
lollipop_plot <- ggplot(aggregate_data, aes(x = Accuracy, y = Category)) +
  geom_segment(aes(xend = 0, yend = Category), color = "#00AEEE", size = 2) +
  geom_point(aes(x = Accuracy, y = Category), color = "#506171", size = 4) +
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 25)) +
  labs(x = "Accuracy (%)", y = NULL, title = "Question Category Accuracy") +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14),
    plot.title = element_text(size = 20, face = "bold"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10)
  ) +
  geom_point(color = "#506171", size = 4)

(ggplotly(lollipop_plot))
```

**Category**
***Multiple Choice**
Students must choose from four answers.

***SPR**
Students must enter their own answer (Student-Produced Response)

```{r - Math Question Domain Accuracy Graph - Specific Domains, out.width='100%'}
# Plot lollipop chart for specific domains
specific_domains <- c("Algebra", "Advanced Math", "Geometry and Trigonometry", "Problem Solving and Data Analysis")
specific_domains_data <- combined_MM %>%
  filter(Question.Domain %in% specific_domains) %>%
  group_by(Question.Domain) %>%
  summarise(Accuracy = mean(Point) * 100)

specific_domains_plot <- ggplot(specific_domains_data, aes(x = Accuracy, y = Question.Domain)) +
  geom_segment(aes(xend = 0, yend = Question.Domain), color = "#00AEEE", size = 2) +
  geom_point(aes(x = Accuracy, y = Question.Domain), color = "#506171", size = 4) +
  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, 25)) +
  labs(x = "Accuracy (%)", y = NULL, title = "Question Domains Accuracy") +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14),
    plot.title = element_text(size = 20, face = "bold"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10)
  ) +
  geom_point(color = "#506171", size = 4)

(ggplotly(specific_domains_plot))

```

**Question Domain** 
***Algebra** 
Students must analyze, solve, and create linear equations and inequalities as well as analyze and solve systems of equations using multiple techniques.

***Advanced Math**
Students must demonstrate skills and knowledge central for successful progression to more advanced math courses, including analyzing, solving, interpreting, and creating equations, including absolute value, quadratic, exponential, polynomial, rational, radical, and other nonlinear equations, as well as analyzing and solving systems of linear and nonlinear equations in two variables. 

***Problem Solving and Data Analysis**
Students must apply quantitative reasoning about ratios, rates, and proportional relationships; understand and apply unit rate; and analyze and interpret one and two-variable data.

***Geometry and Trigonometry**
Students must solve problems that focus on perimeter, area, and volume; angles, triangles, and trigonometry; and circles. 

## Math Module 1
```{r - MM1 Table}
#creating dataframe for the raw score for this section

MM1_rawscore_table

MM1_data <- full_comb %>%
  filter(Source == "MM1", User.email == params$User.email)

filtered_data <- MM1_data %>% 
  filter(grepl("SPR", Question.Domain, ignore.case = TRUE))

MM1_rawscore <- data.frame(
  Attribute = c("Raw Score", "Multiple Choice Raw", "Student-Produced Response Raw"), 
  Points = c(
    sum(MM1_data$Point),
    sum(MM1_data$Point[!grepl("SPR", MM1_data$Question.Domain, ignore.case = TRUE)]),
    sum(filtered_data$Point)
  )
)

#Remove column names and convert to a matrix
colnames(MM1_rawscore) <- NULL

table_matrix <- MM1_rawscore %>% 
  kbl(format = "html") %>% 
  kable_styling(full_width = FALSE) %>% 
  add_header_above(c("Math Module 1" = 2)) %>% 
  row_spec(0, background = "#00AEEE")

#Dropping User.email from table
MM1_scores <- MM1_data %>% 
  ungroup() %>% 
  select(-(c(User.email, User.name, Source)))

MM1_scores %>% 
  kbl(format = "html", escape = FALSE) %>% 
  kable_styling (full_width = T, "striped")%>%
  row_spec(0, background = "#00AEEE") %>%
  row_spec(0:22, align = "c") %>% 
  column_spec(1, bold = T) %>% 
  column_spec(2, background = "#9FE2BF") %>% 
  column_spec(4, background = case_when((MM1_scores$Point == 0) ~ "#F88379", TRUE ~ "white"))
```

## Math Module 2
```{r - MM2 Table}
#creating dataframe for the raw score for this section

MM2_rawscore_table

MM2_data <- full_comb %>% 
  filter(Source == "MM2", User.email == params$User.email)

MM2_rawscore <- data.frame(
  Attribute = c("Raw Score", "Multiple Choice Raw", "Student-Produced Response Raw"), 
  Points = c(
    sum(MM2_data$Point),
    sum(MM2_data$Point[!grepl("SPR", MM2_data$`Question Domain`, ignore.case = TRUE)]),
    sum(MM2_data$Point[grepl("SPR", MM2_data$`Question Domain`, ignore.case = TRUE)])
  )
)

#Remove column names and convert to a matrix
colnames(MM2_rawscore) <- NULL

table_matrix <- MM2_rawscore %>% 
  kbl(format = "html") %>% 
  kable_styling(full_width = FALSE) %>% 
  add_header_above(c("Math Module 2" = 2)) %>% 
  row_spec(0, background = "#00AEEE")

#Dropping User.email from table
MM2_scores <- MM2_data %>% 
  ungroup() %>% 
  select(-(c(User.email, User.name, Source)))

MM2_scores %>% 
  kbl(format = "html", escape = FALSE) %>% 
  kable_styling (full_width = T, "striped")%>%
  row_spec(0, background = "#00AEEE") %>%
  row_spec(0:22, align = "c") %>% 
  column_spec(1, bold = T) %>% 
  column_spec(2, background = "#9FE2BF") %>% 
  column_spec(4, background = case_when((MM2_scores$Point == 0) ~ "#F88379", TRUE ~ "white"))
```

# {-}
